Technical Report

### 2018-03-07 fully-abstract-comp/technical-report.tex
small fix to call implementation
Added a bit more to memory satisfaction. Added comment to remember to update the parts of the LR that 'open' the world
typo.
Update comment.
Updated lro to be assymetric
Update read and write conditions for new worlds.

\begin{align*}
  \src{\Phi} & \; \src{\step \sem{\scall{o}{r_1}{r_2}}(\Phi)} &  &\sourcecolor\left.\arraycolsep=0pt
                                                  \begin{array}[t]{l}
                                                    \text{if }\Phi(\pcreg) = ((\perm,\_),\baddr,\eaddr,\aaddr) \tand \\
                                                    \callCond{\Phi,r_1,r_2,\aaddr} \tand\\
                                                    \baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr \tand \\
                                                    \exec{\Phi(\pcreg)}
                                                  \end{array}\right.\\
  \Phi & \step \sem{\decInstr{\Phi.\mem(\aaddr)}}(\Phi) & &\left.\arraycolsep=0pt
                                                  \begin{array}[t]{l}
                                                    \text{if }\Phi(\pcreg) = ((\perm,\_),\baddr,\eaddr,\aaddr) \tand \\
                                                    \src{(\neg\callCond{\Phi,r_1,r_2,\aaddr} \tor}\\
                                                    \src{\eaddr < \aaddr + \calllen-1) \tand} \\
                                                    \withinBounds{\Phi(\pcreg)} \tand \\
                                                    \exec{\Phi(\pcreg)}
                                                  \end{array}\right.\\
  \Phi& \step \failed & & \totherwise
\end{align*}

@@

    \tstore{\rstk}{42}\\

@@

\[
  \memSatHeap{ms,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{heap} = \pwheap \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{heap}}) \fun \MemSeg \times \MemSeg \wedge \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{heap}})} \pi_2(R_\ms(r)) \wedge \\
      \quad \ms = \biguplus_{r \in \dom(\activeReg{W_\var{heap}})} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{heap}}) \fun \World\ldotp\\
      \qquad W = \oplus_{r \in \activeReg{W_\var{heap}}} R_W(r) \wedge\\
      \qquad \forall r \in \activeReg{W_\var{heap}}, n' < n \ldotp \\
      \qquad \quad \npair[n']{R_\ms(r)} \in  W_\var{heap}(r).H \; W_\var{stack}(r).s \; \xi^{-1}(R_W(r))
    \end{array}
  \right.
\]
}

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
\[
  \lrv(H_\sigma,W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{c_S},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      \npair{(\src{c_S},\sealed{\sigma,\vsc_T})} \in \lrp(W) \wedge \\
      \stpair[.]{c_S}{\vsc_T} \in H_\sigma \; \sigma \; W\wedge \\
      \forall W' \future W, W_o, n' < n, \stpair[.]{c_S'}{\vsc'_T} \in H_\sigma \; \sigma \; W_o \ldotp \\
      \quad \npair[n']{\src{c_S},\src{c_S'},\sealed{\sigma,\vsc_T},\sealed{\sigma,\vsc_T'}} \in \lrexj(W'\oplus W_o) \wedge \\
      \quad \npair[n']{\src{c_S'},\src{c_S},\sealed{\sigma,\vsc_T'},\sealed{\sigma,\vsc_T}} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
%
    % \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    % \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \npair{(\src{\stkptr{\perm,\baddr,\eaddr,\aaddr}}, ((\perm,\linear),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l}
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\linear,W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\linear,W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \npair{(\src{((\perm,\lin),\baddr,\eaddr,\aaddr)}, ((\perm,\lin),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l }
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W}\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W}\\
        \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
                                   \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge\\
                                  \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}\endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

@@

\[
  \readCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, W} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, W}, \ms \ldotp\\
      \quad \dom(\ms) \supseteq [\baddr,\eaddr] \wedge \\
      \quad W(r) \nequal \stareg[(\ms,\ms)]{\pur}
    \end{array}
  \right\}
\]

@@

\[
  \writeCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, W} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr']}{\pur} \wedge \\
      \qquad W(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

@@

    \end{array}
  \]
  \dominique{26-2-2018: $\readCond{\lin,W}$ and $\xReadCond{\lin,W}$ seem contradictory. I suspect the former needs to go?}
\end{theorem}

>>>>

\begin{align*}
  \src{\Phi} & \; \src{\step \sem{\scall{o}{r_1}{r_2}}(\Phi)} &  &\sourcecolor\left.\arraycolsep=0pt
                                                  \begin{array}[t]{l}
                                                    \text{if }\Phi(\pcreg) = ((\perm,\_),\baddr,\eaddr,\aaddr) \tand \\
                                                    \callCond{\Phi,r_1,r_2,\aaddr} \tand\\
                                                    \baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr \tand \\
                                                    \exec{\Phi(\pcreg)}
                                                  \end{array}\right.\\
  \Phi & \step \sem{\decInstr{\Phi.\mem(\aaddr)}}(\Phi) & &\left.\arraycolsep=0pt
                                                  \begin{array}[t]{l}
                                                    \text{if }\Phi(\pcreg) = ((\perm,\_),\baddr,\eaddr,\aaddr) \tand \\
                                                    \src{(\neg\callCond{\Phi,r_1,r_2,\aaddr} \tor}\\
                                                    \src{\eaddr < \aaddr + \calllen-1) \tand} \\
                                                    \withinBounds{\Phi(\pcreg)} \tand \\
                                                    \exec{\Phi(\pcreg)}
                                                  \end{array}\right.\\
  \Phi& \step \failed & & \totherwise
\end{align*}
\dominique{Note: The above does not allow executing code that is on the stack in the source machine, while this is in principle allowed in the target.
This is probably fine if we make sure a stack pointer can never be executable.}

@@

    \tmove{\rtmp{1}}{42}\\
    \tstore{\rstk}{\rtmp{1}}\\

@@

\[
  \memSatHeap{ms,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{heap} = \pwheap \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{heap}}) \fun \MemSeg \times \MemSeg \wedge \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{heap}})} \pi_2(R_\ms(r)) \wedge \\
      \quad \ms = \biguplus_{r \in \dom(\activeReg{W_\var{heap}})} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{heap}}) \fun \World\ldotp\\
      \qquad W = \oplus_{r \in \dom(\activeReg{W_\var{heap}})} R_W(r) \wedge\\
      \qquad \forall r \in \activeReg{W_\var{heap}}, n' < n \ldotp \\
      \qquad \quad \npair[n']{R_\ms(r)} \in  W_\var{heap}(r).H \; W_\var{stack}(r).s \; \xi^{-1}(R_W(r))
    \end{array}
  \right.
\]
}

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
\[
  \lrv(H_\sigma,W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{c_S},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      \npair{(\src{c_S},\sealed{\sigma,\vsc_T})} \in \lrp(W) \wedge \\
      \stpair[.]{c_S}{\vsc_T} \in H_\sigma \; \sigma \; W\wedge \\
      \forall W' \future W, W_o, n' < n, \stpair[.]{c_S'}{\vsc'_T} \in H_\sigma \; \sigma \; W_o \ldotp \\
      \quad \npair[n']{\src{c_S},\src{c_S'},\sealed{\sigma,\vsc_T},\sealed{\sigma,\vsc_T'}} \in \lrexj(W'\oplus W_o) \wedge \\
      \quad \npair[n']{\src{c_S'},\src{c_S},\sealed{\sigma,\vsc_T'},\sealed{\sigma,\vsc_T}} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
%
    % \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    % \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \npair{(\src{\stkptr{\perm,\baddr,\eaddr,\aaddr}}, ((\perm,\linear),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l}
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \npair{(\src{((\perm,\lin),\baddr,\eaddr,\aaddr)}, ((\perm,\lin),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l }
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W}\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W}\\
        \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
                                   \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge\\
                                  \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}\endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

@@

\[
  \readCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, W}, \ms \ldotp\\
      \quad \dom(\ms) \supseteq [\baddr,\eaddr] \wedge \\
      \quad W(r) \nequal \stareg[(\ms,\ms)]{\pur}
    \end{array}
  \right\}
\]

@@

\[
  \writeCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr']}{\pur} \wedge \\
      \qquad W(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackWriteCond{W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr']}{\pur} \wedge \\
      \qquad W(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

@@

    \end{array}
  \]
  \dominique{6-3-2018: $\readCond{\lin,W}$ and $\xReadCond{\lin,W}$ seem contradictory.
    I suspect the latter needs to go? I suspect we don't need to assume the context has no way to modify its own code.}
\end{theorem}
